\thispagestyle{empty}

\begin{center}
    {\LARGE\bf Abstract}
\end{center}

\noindent
The aim of Location Sensitive Social Notifier is to give a platform for location based messaging, which should enable members of the public or companies to portray messages that then can be viewed when an individual is near to the message. This is a lucrative platform that could be used between friends or as an advertising platform for companies that want to sell their wears. There are many possibilities for the application, many of which we do not know yet, but each user will find their own unique niche to fill with the application.\\
\\
The project aims to create a platform that requires no extra hardware and that can be run from a standard Google Android smart phone with just the use of GPS to determine where the device is placed. Platform wise, the project uses a mixture of the stock Android SDK \cite{Google:androidAPIDocs:2015:online} for the front end application, Node.js\cite{nodeteam:node:2015:online} with the HAPI.js\cite{hapiteam:hapti:2015:online} framework for the middle tier application and a PostgreSQL\cite{Postgres:APIDocumentation:2015:online} database for the database tier of the application. With the use of advanced GPS tracking the application can detect when there is a message nearby to the user and ping up a notification within the Google Android UI to notify the user of the nearby message. They can then interact with the message that has been left by either commenting or voting on it. This should engage a community atmosphere around messages.\\ 
\\
Soon Location Sensitive Social Notifier will be available on the Google Play Store and the platform will be available to millions of possible users. This will hopefully be a very exciting platform that allows users to share messages and will grow into an interesting community that people want to be a part of.