\thispagestyle{empty}

\begin{center}
{\LARGE\bf Acknowledgements}

I would like to dedicate my dissertation to Linda Hatfield, my Great Aunt, who has helped with moral support and encouragement throughout my degree. Her kind words have kept me determined to achieve the goal of completing this degree.

% Family
Next I would like to acknowledge my family, and especially my parents for raising me and supporting me whilst giving me the opportunity to do a degree in a subject that I am passionate about.

Angela \& Mark Rosier

My brothers and their partners for being there throughout:

\begin{tabular}{ l r }
Jonathan \& Eleri Rosier & Matthew Rosier \& Stephanie Fruen.\\
\end{tabular}

\vspace{3mm}

Next we move on to the non-family and I will start with the people that have kept me on track through my life so far. I must deeply thank these two people for being there whenever I needed them and always enabling me to do my best, even when times got tough. Thank you!

\begin{tabular}{ l r }
Daniel Brothers & Claire Mollart\\
\end{tabular}

\vspace{3mm}

% Oracle
I would like to acknowledged my former coworkers and friends from Oracle for their input and support throughout my industrial placement and the early formulations of the idea for this project.

\begin{tabular}{ l c r }
Peter Woodward & James Atkinson & James Maher\\
\end{tabular}

\vspace{3mm}

Honorable mention to my non-computer science friends for their support and encouragement throughout my degree:

% Old buddies
\begin{tabular}{ l c r }
Karl Brown & Cian O'Shaughnessy & Matthew Osborne\\
\end{tabular}

% Others Aber people
\begin{tabular}{ l c c r }
Charlotte Ford & Daniel Jones & Thomas Nicolaides & Chloe Major\\
\end{tabular}

\vspace{3mm}

% Staff
I must acknowledge my Study Skills Tutor and Student Mentor for all their help throughout my degree. I could not have got here without them:

\begin{tabular}{ l r }
Alison Nash & Mary Glasser\\
\end{tabular}

\vspace{3mm}

% Main Comp Sci
I would like to thank all of my fellow Computer Science students. The following are honorable mentions as they have been great friends: 

\begin{tabular}{ l c c r }
Samuel Sherar & Samuel Clements & Samuel Nicholls & Samuel Jackson \\
Alexander Stuart & Victoria Haxness & Natalia Miller & Helen Harman \\
Christopher Savill & Christopher Marriott & Roberto Fajardo & Jonathon Shire \\
Gavin Wilson & Andrew Cooper & Scott Roe & Nicholas Pattern \\ 
\end{tabular}

\vspace{3mm}

Last but not least I would like to thank the following teaching fellows and lecturers for their help and advice throughout this project:

\begin{tabular}{ l c c r }
Neil Taylor & David Price & Christopher Loftus & Andrew Starr\\
\end{tabular}

\vspace{3mm}

Thank you for the 4 best years of my life.
\end{center}